Response to the defense feedback

### 2021-06-04 Chapter-1/Chapter-1.tex
Updates from Overleaf

\chapter{Introduction} \label{chapter1}
\section{Side-channels}
A side-channel attack is any attack that allows adversaries to infer sensitive information based on ``side-channel'' information. In 1996, Kocher published the first side-channel attack in the literature~\cite{kocher1996timing}. He demonstrated that an attacker could break cryptosystems such as RSA or Diffie-Hellman by measuring the execution time of a simple modular exponentiation operation. The simple modular exponentiation calculates the remainder of an exponent divided by an integer.  The simple modular exponentiation operation executes faster when the exponent bit is 0 and slower when the exponent bit is 1. As a result, an attacker can infer the whole secret key by measuring the execution time of the operation. Since then, researchers have proposed numerous side-channel attacks which exploit different kinds of ``side-channel'' information, including execution timing~\cite{184415,disselkoen2017prime+}, power consumption~\cite{kar20178}, electromagnetic radiation~\cite{agrawal2002side,217605}, and even sound~\cite{chari1999towards}.

@@

\begin{figure}[h]
    \begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
static char FSb[256] = {...}
... 
uint32_t a = *RK++ ^ \ 
(FSb[(secret)) ^
(FSb[(secret >> 8)] << 8 ) ^
(FSb[(secret >>16)] << 16 ) ^
(FSb[(secret >>24)] << 24 );
...
\end{lstlisting}
    \caption{Secret-dependent data accesses}
    \label{fig:secret:da}
\end{figure}

@@

\begin{itemize}
    \item We propose a method that can quantify fine-grained leaked information from side-channel vulnerabilities that result from actual attack scenarios in a single trace attack. Our approach differs from previous ones in that we precisely calculate the amount of leakage. We model the information quantification problem as a counting problem and use a Monte Carlo sampling method to estimate the information leakage.
    \item We implement the method into a tool and apply it to several pieces of real software. \tool{}\footnote{Abacus is open source under the MIT license.  \url{https://github.com/s3team/Abacus}} successfully identifies previous unknown and known side-channel vulnerabilities and calculates the corresponding information leakage. Our results are useful in practice. The leakage estimates and the corresponding inputs that triggers the vulnerability can help developers triage and fix the vulnerabilities.
\end{itemize}

>>>>

\chapter{Introduction} \label{chapter1}
\section{Side-channels}
A side-channel attack is any attack that allows adversaries to infer sensitive information based on ``side-channel'' information. In 1996, Kocher published the first side-channel attack in the literature~\cite{kocher1996timing}. He demonstrated that an attacker could break cryptosystems such as RSA or Diffie-Hellman by measuring the execution time of a simple modular exponentiation operation. The simple modular exponentiation calculates the remainder of an exponent divided by an integer.  The simple modular exponentiation operation executes faster when the exponent bit is 0 and slower when the exponent bit is 1. As a result, an attacker can infer the whole secret key by measuring the execution time of the operation. Since then, researchers have proposed numerous side-channel attacks which exploit different kinds of ``side-channel'' information, including execution timing~\cite{184415,disselkoen2017prime+,7163050}, power consumption~\cite{kar20178}, electromagnetic radiation~\cite{agrawal2002side,217605}, and even sound~\cite{chari1999towards}.

@@

\begin{figure}[h]
    \begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
static char FSb[256] = {...}
... 
uint32_t a = *RK++ ^ \ 
(FSb[(secret)) ^
(FSb[(secret >> 8)] << 8 ) ^
(FSb[(secret >>16)] << 16 ) ^
(FSb[(secret >>24)] << 24 );
...
\end{lstlisting}
    \caption{Secret-dependent data access}
    \label{fig:secret:da}
\end{figure}

@@

\begin{itemize}
    \item We propose a method that can quantify fine-grained leaked information from side-channel vulnerabilities that result from actual attack scenarios in a single trace attack. Our approach differs from previous ones in that we precisely calculate the amount of leakage. We model the information quantification problem as a counting problem and use a Monte Carlo sampling method to estimate the information leakage.
    \item We implement the method into a tool called \tool{} and apply it to several pieces of real software. \tool{}\footnote{Abacus is open source under the MIT license.  \url{https://github.com/s3team/Abacus}} successfully identifies previous unknown and known side-channel vulnerabilities and calculates the corresponding information leakage. Our results are useful in practice. The leakage estimates and the corresponding inputs that triggers the vulnerability can help developers triage and fix the vulnerabilities.
\end{itemize}
